### 2021-07-21 paper/paper.tex
tweak PID figure slightly

\begin{figure}
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (seconds)},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.2e-6,
          grid=major,
        ]
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak.dat};
        %   \addlegendentry{\texttt{TreeMesh} (Trixi.jl)}
        \addplot[blue, mark=*, solid]
          table [x index=0, y index=3]{../data/pids_euler_weak.dat};
          \addlegendentry{\footnotesize FLUXO}
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak.dat};
          % \addlegendentry{\texttt{StructuredMesh} (Trixi.jl)}
          \addlegendentry{\footnotesize Trixi.jl}
        \node at (axis cs:13,3.5e-7) {Weak form};

        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha.dat};
        \addplot[blue, mark=*, dashed]
          table [x index=0, y index=3]{../data/pids_euler_ranocha.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha.dat};
        \node [rotate=23] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:7.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          ymin=0.0,
          ymax=1.1,
          ytick={0,0.25,0.5,0.75,1},
          grid=major,
        ]
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak_relative.dat};
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak_relative.dat};
        \addplot[blue, mark=*, solid]
          table [x index=0, y index=3]{../data/pids_euler_weak_relative.dat};

        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
        \addplot[blue, mark=*, dashed]
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};

        % \node at (axis cs:10,0.6) {Will be improved soon};
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}

>>>>

\begin{figure}
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (seconds)},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.2e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid]
          table [x index=0, y index=3]{../data/pids_euler_weak.dat};
          \addlegendentry{FLUXO}
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak.dat};
        %   \addlegendentry{\texttt{TreeMesh} (Trixi.jl)}
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak.dat};
          % \addlegendentry{\texttt{StructuredMesh} (Trixi.jl)}
          \addlegendentry{Trixi.jl}
        \node at (axis cs:13,3.5e-7) {Weak form};

        \addplot[blue, mark=*, dashed]
          table [x index=0, y index=3]{../data/pids_euler_ranocha.dat};
        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha.dat};
        \node [rotate=23] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:7.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0,0.25,0.5,0.75,1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot]
          table [x index=0, y index=3]{../data/pids_euler_weak_relative.dat};
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak_relative.dat};
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak_relative.dat};
          \addlegendentry{Weak form}

        \addplot[blue, mark=*, dashed, forget plot]
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}
